Designing a high-performance boundary element library with OpenCL and Numba

### 2021-05-28 numba.tex
Have written reviewer responses
Updated references and merged files

\section{NUMBA ASSEMBLY OF INTEGRAL OPERATORS}
The main focus of Numba within Bempp-cl is to provide accelerated implementations of routines with linear complexity, such as grid iterations, integration of functions over grids, or assembly of certain sparse matrices. However, we also provide a fall-back implementation of the OpenCL dense operator assembly in Numba.

With Numba, we use loop parallelism: each loop iteration is the assembly of one test triangle with all trial triangles. We then parallelize over the test triangles.
All such assemblies are executed through a parallel for-loop.
Within each loop we try to optimize for auto-vectorization by linearly passing through the data in memory order for the individual operations. However, a much smaller fraction of operations is SIMD optimized due to the lack of targeted SIMD constructs in Numba.

>>>>

\section{NUMBA ASSEMBLY OF INTEGRAL OPERATORS}
The main focus of Numba \cite{numba} within Bempp-cl is to provide accelerated implementations of routines with linear complexity, such as grid iterations, integration of functions over grids, or assembly of certain sparse matrices. However, we also provide a fall-back implementation of the OpenCL dense operator assembly in Numba.

With Numba, we use loop parallelism: each loop iteration is the assembly of one test triangle with all trial triangles. We then parallelize over the test triangles through a parallel for-loop.
Within each loop we try to optimize for auto-vectorization by linearly passing through the data in memory order for the individual operations. However, a much smaller fraction of operations is SIMD optimized due to the lack of targeted SIMD constructs in Numba.
